Implementation and Analysis of Homomorphic Facial Image Encryption and Manipulation

### 2019-02-10 paper/paper-conf.tex
Cleaned up and shortened Ch1,2

\section{Introduction}
\subsection{Context of the Study}
Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}. To meet these needs, various cryptosystems have been developed. A cryptosystem is a system which operates on plaintexts, ciphertexts and keys using an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key~\cite{bauer_cryptosystem_2005}. The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key. This allows data to be securely transmitted over an insecure channel. Much research has been done on the development and application of various cryptosystems.

@@

In a homomorphic cryptosystem, operations such as addition and multiplication can be performed on encrypted data. These operations are then preserved when the data is decrypted. In this manner, data is manipulated without compromising data privacy, as the encrypted data being operated on remains secure~\cite{fontaine_survey_2007, sen_homomorphic_2013}. While numerous homomorphic cryptosystems exist for use with digital data in general, in the area of homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}. More advanced operations have also been implemented using homomorphic cryptosystems, such as facial recognition \cite{hutchison_privacy-preserving_2009} and neural networks \cite{hesamifard_cryptodl:_2017}. This study in particular focuses on facial recognition.

@@

\subsection{Research Objectives}
Previous attempts in the literature to provide image processing tasks such as image manipulation \cite{ziad_cryptoimg:_2016} and  facial recognition \cite{hutchison_privacy-preserving_2009} have primarily used the Paillier and  Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystems to perform linear operations on encrypted data. In this study, we extend this research to provide an objective comparison of various homomorphic cryptosystems currently in the literature in performing non-linear operations, as opposed to just linear operations, and facial detection, as opposed to just facial recognition.

Our main research objective is to assess the practicality of various homomorphic cryptosystems with regard to image processing on faces. Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}. Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed efficiently~\cite{li_elliptic_2012}.

In summary, in this study, we wish to
\begin{enumerate}
    \item Implement common image processing operations using known homomorphic encryption schemes, then determine which schemes admit more image processing operations and extend known cryptosystems to support more operations, if possible;
    \item Compare the time efficiency and accuracy of common image processing operations under known homomorphic encryption schemes, and of common image processing operations without using homomorphic encryption;
    \item Create a library to allow for convenient use and comparison of these homomorphic encryption schemes for image processing and facial recognition.
\end{enumerate}

\subsection{Scope and Limitations}
Our study will be limited in terms of the cryptosystems to be tested, the image processing operations we will implement, and the statistical tests we will use to gauge the security of the cryptosystems. Below is a listing of the scope of the study.

We will implement and test the following algorithms:
\begin{enumerate}
	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
    \item The Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is primarily used for secure integer comparison.
	\item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
	\item The Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren, and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Non-linear image intensity adjustment (logarithm and power-log transformations)
	\item Facial detection and recognition using the eigenface approach \cite{turk_eigenfaces_1991}.
\end{enumerate}
We will adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et. al~\cite{ahmed_benchmark_2016}. The presented benchmark reflects many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
    \item Mean Squared Error (MSE)
    \item Peak Signal to Noise Ratio (PSNR)
    \item Structural Similarity Index (SSIM)
\end{enumerate}
A detailed overview of the above will be provided in the methodology. Grayscale images will be used in the study.
A client-server model for secure computation will be assumed to allow operations such as secure comparison and exponentiation.
Training and test data are taken from the publicly available \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.

@@

% In other words, 
A homomorphic cryptosystem preserves the operations that can be done with the plaintext without requiring an intermediary step of decrypting the ciphertext beforehand. It is important to note that the operations $\boxplus$ and $\boxdot$ need not be the same. A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.

@@

\subsection{Partially Homomorphic Cryptosystems}
In this section, we will present two classical partially homomorphic cryptosystems which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem. Both of these cryptosystems encrypt integer plaintexts and are additively homomorphic.

We will then show that the cryptosystems can be modified to support privacy-perserving polynomial evaluation in a client-server protocol: given an encrypted message $m$, evaluate $f(m)$ where $f$ is a polynomial function.

\subsubsection{The Paillier Cryptosystem}
The Paillier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Paillier, is a probabilistic encryption scheme which is based on the composite residuosity class problem. The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic. 
% We now state the encryption and decryption algorithms of the Paillier cryptosystem and its homomorphic properties.

@@

\paragraph{Homomorphic Properties of the Paillier Cryptosystem}
The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively. They are defined as follows.

For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{align*}
  D(E(m_1)g^k\bmod n^2) &=(m_1+k)\bmod n\\
  D(E(m_1)E(m_2)\bmod n^2) &=(m_1+m_2)\bmod n\\
  D(E(m_1)^k\bmod n^2) &= km_1\bmod n
\end{align*}

\subsubsection{The DGK Cryptosystem}
The DGK cryptosystem was published by Damg{\aa}rd, Geisler, and Kr{\o}igaard in 2007 in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is widely used in the literature \cite{veugen_improving_2012}.

@@

\paragraph{Homomorphic Properties of the DGK Cryptosystem}
The DGK cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively. They are defined as follows.

For all $m_1,m_2 \in \mathbb{Z}_u$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{align*}
    D(E(m_1)g^k) &=(m_1+k)\bmod u\\
    D(E(m_1)E(m_2)) &=(m_1+m_2)\bmod u\\
    D(E(m_1)^k) &= km_1\bmod u
\end{align*}

As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
\begin{proof}
  Let $m \in \mathbb{Z}_u$ and $k\in \mathbb{N}$.
  We consider $E(m)^k = (g^m \cdot h^r \bmod{n})^k\bmod n$.
  \begin{align*}
    (g^m \cdot h^r \bmod{n})^k \bmod n
    &= (g^m \cdot h^r)^k \bmod{n}\\
    &= (g^m)^k \cdot (h^r)^k \bmod{n}\\
    &= g^{km} \cdot (h^kr) \bmod{n}\\
  \end{align*}
  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^kr) \bmod{n} = D(E(m_1)^k)$ is a valid encryption of the message $km$.
\end{proof}

\subsubsection{Secure Exponentiation and Multiplication Protocols}
\label{ssec:exponentiationprotocol}
[TO-DO: This is further explained in another paper.]
% In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.

@@

% We will present two such cryptosystems, the Dasgupta--Pal cryptosystem, which we present in full to explain a correction we propose to it, and the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.
We will present the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.

@@

\subsubsection{HElib and the BGV Cryptosystem}
The BGV (Brakerski--Gentry--Vaikuntanathan) cryptosystem \cite{cryptoeprint:2011:277} is a fully homomorphic cryptosystem created based on the ring-learning with error problem. The BGV cryptosystem was constructed to surpass the limitations of prior fully homomorphic cryptosystems, which were based on the first fully homomorphic cryptosystem by Gentry \cite{gentry_fully_2009}.

@@

\subsection{Image Intensity Transformations}
We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$. We use $R(x,y)$ to represent the entry at the $x$th row and $y$th column of a matrix $R$.
An intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$. This function is then applied to every pixel in $R$.
The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control.

@@

\subsection{Facial Detection and Recognition}
%% TODO: Brian dump ur stuff here

@@

The protocol for squaring a number as described earlier is a workaround for the limitations of Paillier or any other partially homomorphic cryptosystem that only supports addition and scalar multiplication. This can be possibly extended so that operations such as pairwise multiplication and exponentiation are also supported, provided that the protocol involves two parties.

@@

\section{Methodology}
In this study we apply four homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, dasgupta_design_2016, garay_algorithms_2014} for use in image processing and facial recognition applications.
While the Paillier and DGK cryptosystems have been implemented for use in image processing in~\cite{ziad_cryptoimg:_2016, hutchison_privacy-preserving_2009}, the other cryptosystems have to be adapted for this study.
Two experiments are conducted in this study:
\begin{enumerate}
	\item Assessment of non-linear image intensity transformations under each of the four cryptosystems.
	\item Assessment of efficiency of each of the four cryptosystems when applied for use in privacy-preserving facial recognition and detection using eigenfaces.
\end{enumerate}
The results of the image intensity transformations are tested for image quality using benchmarks in~\cite{ahmed_benchmark_2016}.

@@

For convenience, a wrapper library is created that integrates the four cryptosystems into a unified interface.

\subsection{Secure Computation with Real Numbers}
[TO-DO: This is further explained in another paper.]
% We will briefly discuss a protocol to enable cryptosystems built for integer inputs to handle real number inputs.
% The following protocol was also used by \textit{CryptoImg} for image processing \cite{ziad_cryptoimg:_2016}.
% This is also used for our own implementation of the Dasgupta--Pal cryptosystem in order to handle real numbers.

@@

\subsection{Non-Linear Intensity Transformations}
Aside from implementing the homomorphic encryption and decryption algorithms, we will also implement library functions for image negation, logarithm transformation and power-law transformation, as they are defined in~\cite{gonzalez_digital_2008}.
We now describe how we implement the logarithm and power-law image intensity transformations. In the case of partially homomorphic cryptosystems (Paillier, DGK), if  exponentiation and multiplication is required, the secure protocols in section \ref{ssec:exponentiationprotocol} will be used.

>>>>

\section{Introduction}
\subsection{Context of the Study}
Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}. To meet these needs, various cryptosystems have been developed. A cryptosystem is a system which operates on plaintexts, ciphertexts and keys using an encryption algorithm, which maps a plaintext to a ciphertext, together with a decryption algorithm, which maps a ciphertext to a plaintext, given an appropriate key~\cite{bauer_cryptosystem_2005}. The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key. This allows data to be securely transmitted over an insecure channel.

@@

In a homomorphic cryptosystem, operations such as addition and multiplication can be performed on encrypted data. These operations are then preserved when the data is decrypted. In this manner, data is manipulated without compromising data privacy, as the encrypted data being operated on remains secure~\cite{fontaine_survey_2007, sen_homomorphic_2013}. In the area of homomorphic image encryption, there is interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}. More advanced operations have also been implemented using homomorphic cryptosystems, such as facial recognition \cite{hutchison_privacy-preserving_2009} and neural networks \cite{hesamifard_cryptodl:_2017}. This study in particular focuses on facial recognition.

@@

\subsection{Research Objectives}
% Previous attempts in the literature to provide image processing tasks such as image manipulation \cite{ziad_cryptoimg:_2016} and  facial recognition \cite{hutchison_privacy-preserving_2009} have primarily used the Paillier and  Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystems to perform linear operations on encrypted data. 
% In this study, we extend this research to provide an objective comparison of various homomorphic cryptosystems currently in the literature in performing non-linear operations, and facial detection, as opposed to just linear operations and facial recognition.

Our main research objective is to assess the practicality of various homomorphic cryptosystems with regard to image processing on faces. 
% Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}. Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed efficiently~\cite{li_elliptic_2012}.

% In summary, in this study, we wish to
More specifically, we wish to do the following:
\begin{enumerate}
    \item Implement common linear and non-linear image processing operations using known homomorphic encryption schemes, then determine which schemes admit more image processing operations and extend known cryptosystems to support more operations, if possible;
    \item Compare the time efficiency and accuracy of common image processing operations under known homomorphic encryption schemes, and of common image processing operations without using homomorphic encryption;
    \item Create a library to allow for convenient use and comparison of these homomorphic encryption schemes for image processing and facial recognition.
\end{enumerate}

\subsection{Scope and Limitations}
% Our study will be limited in terms of the cryptosystems to be tested, the image processing operations we will implement, and the statistical tests we will use to gauge the security of the cryptosystems. Below is a listing of the scope of the study.

% We will implement and test the following algorithms:
In this study, we will implement and test the following cryptosystems:
\begin{enumerate}
	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
    \item The Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is primarily used for secure integer comparison.
	% \item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
	\item The Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren, and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Non-linear image intensity adjustment (logarithm and power-log transformations)
	\item Facial detection and recognition using the eigenface approach \cite{turk_eigenfaces_1991}.
\end{enumerate}
We will adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et. al~\cite{ahmed_benchmark_2016}. The presented benchmark reflects many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
    \item Mean Squared Error (MSE)
    \item Peak Signal to Noise Ratio (PSNR)
    \item Structural Similarity Index (SSIM)
\end{enumerate}
A detailed overview of the above will be provided in the methodology. Grayscale images will be used in the study.
A client-server model for secure computation will be assumed to allow operations such as secure comparison and exponentiation.
Training and test data are taken from the publicly available \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.

@@

% In other words, 
A homomorphic cryptosystem preserves the operations that can be done with the plaintext without requiring an intermediary step of decrypting the ciphertext beforehand. It is important to note that the operations in the plaintext space and ciphertext space need not be the same. A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.

@@

\subsection{Partially Homomorphic Cryptosystems}
In this section, we will present two classical partially homomorphic cryptosystems which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem. Both of these cryptosystems encrypt integer plaintexts as integer ciphertexts. In our description of each cryptosystem, we use $E(m)$ to denote the encryption of a plaintext $m$, and $D(c)$ to denote the decryption of a ciphertext $c$.

% We will then show that the cryptosystems can be modified to support privacy-perserving polynomial evaluation in a client-server protocol: given an encrypted message $m$, evaluate $f(m)$ where $f$ is a polynomial function.

\subsubsection{The Paillier Cryptosystem}
The Paillier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Paillier, is a probabilistic encryption scheme which is based on the composite residuosity class problem. The scheme has several well--known homomorphic properties.
% The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic.
% We now state the encryption and decryption algorithms of the Paillier cryptosystem and its homomorphic properties.

@@

% \paragraph{Homomorphic Properties of the Paillier Cryptosystem}
% The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively. They are defined as follows.

For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold for the Paillier cryptosystem with public key $(g,n)$.
\begin{align*}
  D(E(m_1)g^k\bmod n^2) &=(m_1+k)\bmod n\\
  D(E(m_1)E(m_2)\bmod n^2) &=(m_1+m_2)\bmod n\\
  D(E(m_1)^k\bmod n^2) &= km_1\bmod n
\end{align*}

These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively.

\subsubsection{The DGK Cryptosystem}
The DGK cryptosystem was published by Damg{\aa}rd, Geisler, and Kr{\o}igaard in 2007 in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is widely used in the literature \cite{veugen_improving_2012}. 
The DGK cryptosystem has homomorphic properties similar to the Paillier cryptosystem.

@@

% \paragraph{Homomorphic Properties of the DGK Cryptosystem}
% The DGK cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively. They are defined as follows.

For all $m_1,m_2 \in \mathbb{Z}_u$ and $k\in \mathbb{N}$, the following homomorphic properties hold for the DGK cryptosystem with public key $(n,g,h,u)$.
\begin{align*}
    D(E(m_1)g^k) &=(m_1+k)\bmod u\\
    D(E(m_1)E(m_2)) &=(m_1+m_2)\bmod u\\
    D(E(m_1)^k) &= km_1\bmod u
\end{align*}

As the multiplicative homomorphism was not presented in the original paper, we provide a short proof here.
\begin{proof}
  Let $m \in \mathbb{Z}_u$ and $k\in \mathbb{N}$.
  We consider $E(m)^k = (g^m \cdot h^r \bmod{n})^k\bmod n$.
  \begin{align*}
    (g^m \cdot h^r \bmod{n})^k \bmod n
    &= (g^m \cdot h^r)^k \bmod{n}\\
    &= (g^m)^k \cdot (h^r)^k \bmod{n}\\
    &= g^{km} \cdot (h^kr) \bmod{n}
  \end{align*}
  Since $r$ is a random integer, $kr$ is also a random integer, Therefore, $g^{km} \cdot (h^kr) \bmod{n} = D(E(m_1)^k)$ is a valid encryption of the message $km$.
\end{proof}

% \subsubsection{Secure Exponentiation and Multiplication Protocols}
% \label{ssec:exponentiationprotocol}
% [TO-DO: This is further explained in another paper.]
% In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.

@@

% We will present two such cryptosystems, the Dasgupta--Pal cryptosystem, which we present in full to explain a correction we propose to it, and the BGV cryptosystem, which has open source implementations availble primarily used in homomorphic cryptography research.

@@

% \subsubsection{HElib and the BGV Cryptosystem}
The BGV (Brakerski--Gentry--Vaikuntanathan) cryptosystem \cite{cryptoeprint:2011:277} is a fully homomorphic cryptosystem created based on the ring-learning with error problem. The BGV cryptosystem was constructed to surpass the limitations of prior fully homomorphic cryptosystems, which were based on the first fully homomorphic cryptosystem by Gentry \cite{gentry_fully_2009}.

@@

\subsection{Image Intensity Transformations}
We represent a digital image $R$ as an $M \times N$ matrix of pixel intensity values, each value in the range $\left[0, L-1\right]$, for some positive integer $L$. We denote with $R(x,y)$ the entry at the $x$th row and $y$th column of a matrix $R$.
An intensity transformation on an image $R$ can be defined as a function $T$ which maps a pixel value $r$ to a new value $r^\prime$, which we can write as $r^\prime = T\left(r\right)$. This function is then applied to every pixel in $R$.
The \textit{CryptoImg} library implemented two types of linear intensity transformations: image negation and brightness control.

@@

\subsection{Facial Detection and Recognition}

@@

The protocol for squaring a number as described earlier is a workaround for the limitations of Paillier or any other partially homomorphic cryptosystem that only supports addition and scalar multiplication. 
% This can be possibly extended so that operations such as pairwise multiplication and exponentiation are also supported, provided that the protocol involves two parties.

@@

\section{Methodology}
In this study we apply three homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, garay_algorithms_2014} for use in image processing and facial recognition applications.
While the Paillier and DGK cryptosystems have been implemented for use in image processing in~\cite{ziad_cryptoimg:_2016, hutchison_privacy-preserving_2009}, the other cryptosystems have to be adapted for this study.
Two experiments are conducted in this study:
\begin{enumerate}
	\item Assessment of non-linear image intensity transformations under each of the four cryptosystems.
	\item Assessment of efficiency of each of the four cryptosystems when applied for use in privacy-preserving facial recognition and detection using eigenfaces.
\end{enumerate}
The results of the image intensity transformations are tested for image quality using benchmarks in~\cite{ahmed_benchmark_2016}.

@@

For convenience, a wrapper library is created that integrates the three cryptosystems into a unified interface.

\subsection{Extension of Partially Homomorphic Cryptosystems}
\label{sse:pheextension}
[TO-DO: This is further explained in another paper.]
% We will briefly discuss a protocol to enable cryptosystems built for integer inputs to handle real number inputs.
% The following protocol was also used by \textit{CryptoImg} for image processing \cite{ziad_cryptoimg:_2016}.
% This is also used for our own implementation of the Dasgupta--Pal cryptosystem in order to handle real numbers.

@@

\subsection{Non-Linear Intensity Transformations}
We will implement library functions for image negation, logarithm transformation and power-law transformation, as they are defined in~\cite{gonzalez_digital_2008}.
We now describe how we implement the logarithm and power-law image intensity transformations. In the case of partially homomorphic cryptosystems (Paillier, DGK), if exponentiation and multiplication is required, the secure protocols in section \ref{ssec:pheextension} will be used.
